%_________Appendix__________________________________
\ifLSRITRtutorial
	\chapter{BUSTED! Last chance to actually read the HowTo-Section!!}
	
	Make sure your thesis is well structured, that each major section does what it is supposed to do, and that the whole thing hangs together. The basic structure is often as given in this template (but other structures are possible). In particular, don't think you need to have exactly as many major sections or chapters as the list implies; sometimes it makes sense to merge things, sometimes it makes sense to move things (e.g., the literature review is in many papers deferred until after the results), sometimes it makes sense to split a logical part into several individual sections. Just use some common sense.
	
	Hand in your thesis at minimum \textbf{one week} before the deadline for correction. You will receive feedback for the final version and very likely have to do minor or major revisions of your writing. Plan your writing schedule to allow for these adjustments, which can have quite some impact on your grade! 
	
	\optional{Please have a look on our \href{https://wiki.lsr.ei.tum.de/thesiswriting_students}{thesis-guidelines} as well before submitting your \emph{final} thesis.}
	
	\section{Style and Expressions}
	
	Before handing in your thesis, even for an intermediate review, please perform a spellcheck and correct grammar mistakes. The report is not meant to be a narrative text. Please stick to neutral and technical style and avoid subjective or biased expressions or adjectives/adverbs such as \emph{obviously, always, very, especially well, actually, so-called etc}. Scientific writing is about precision and you should underpin your statements factually, not soften them with unnecessary qualifiers.
	
	... Okay enough. But please check chapter \ref{sec:Tutorial} before starting with your report. 
\fi