\begin{thebibliography}{9}
\bibitem{Qingchen} 
Qingchen Liu, Mengbin Ye, Zhiyong Sun, Jiahu Qin, and Changbin Yu.
\textit{Coverage control of unicycle agents under constant speed constraints}. 
IFAC-PapersOnLine, 50(1):2471{2476, 2017}.

\bibitem{Jorge} 
Jorge Cortes, Sonia Martinez, Timur Karatas, Francesco Bullo and \textit{Member IEEE}.
\textit{Coverage control for mobile sensing networks}. 
IEEE Transactions on Robotics and Automation.

\bibitem{Schwager} 
Mac Schwager.
\textit{A Gradient Optimization Approach to Adaptive Multi-Robot Control}. 
Ph.D. thesis, Massachusetts Institute of Technology.

\bibitem{Keng} 
Keng Peng Tee and Shuzhi Sam Ge
\textit{Control of Nonlinear Systems with Full State Constraint Using A
	Barrier Lyapunov Function}. 
Joint 48th IEEE Conference on Decision and Control and 28th Chinese Control Conference

\bibitem{Lee} 
Sung G. Lee and Magnus Egerstedt, Fellow, IEEE
\textit{Multi-Robot Control Using Time-Varying Density Functions}. 
IEEE Transactions on Robotic

\bibitem{ChengSong} 
Cheng Song, Lu Liu, Gang Feng.
\textit{Coverage control for homogeneous mobile sensors with input constraints on a unit circle}. 
Unmanned Systems, 4(01):15{21, 2016}.

\bibitem{Nguyen} 
Thien-Minh Nguyen, Xiuxian Li, Lihua Xie
\textit{Barrier Coverage by Heterogeneous Sensor Network with Input Saturation}. 
978-1-5090-1573-3/17/

\bibitem{Zhang} 
Zhang Jingxin, Zhou Pan, Ma Lei
\textit{Coverage Control of Multiple Heterogeneous Mobile Robots with Nonholonomic Constraints }. 
Proceedings of the 35th Chinese Control Conference

\bibitem{Zhang} 
Jun Xu, Jinwen Hu, Lihua Xie, Kai-Yew Lum
\textit{Distributed Coverage Control Under Generalized Locational Optimization Framework}. 
Proceedings of the 31st Chinese Control Conference

\bibitem{Flanders} 
Harley Flanders
\textit{Differentiation Under the Integral Sign}. 
The American Mathematical Monthly Vol. 80, No. 6 (Jun. - Jul., 1973), pp. 615-627

\bibitem{J. Wolff, M. Buss} 
J. Wolff, M. Buss
\textit{Invariance Control Design For Nonlinear Control Affine Systems Under Hard State Constraints}. 
IFAC Nonlinear Control Systems

\bibitem{Qiang Du} 
Qiang Du, Vance Faber and Max Gunzburger
\textit{Centroidal Voronoi Tessellations: Applications and Algorithms}. 
SIAM Review, Vol. 41, No. 4 (Dec., 1999), pp. 637-676

\bibitem{Qiang Du} 
Qiang Du; and Maria Emelianenko2;
\textit{Acceleration Schemes for Computing Centroidal Voronoi Tessellations}. 
NUMERICAL LINEAR ALGEBRA WITH APPLICATIONS. Numer. Linear Algebra Appl. 2006, 13 173 - 192

\bibitem{Song} 
Chanyoung Song, Jehyun Cha, Mokwon Lee, and Deok-Soo Kim
\textit{Dynamic Voronoi Diagram for Moving Disks}. 
DOI 10.1109/TVCG.2019.2959321, IEEE

\bibitem{Ichihara} 
Hiroyuki Ichihara, and Eitaku Nobuyama
\textit{Stability Analysis and Control Design of Linear Systems with Input Saturation Using Matrix Sum of Squares Relaxation}. 
5th IFAC Symposium on Robust Control Design

\bibitem{Takagi} 
Natsuki Takagi, Takeshi Nishida and Toshihiro Kobayashi
\textit{A Design of Adaptive Control Systems with Input Saturation}. 
SICE-ICASE International Joint Conference 2006

\bibitem{Chaoui} 
F. Z. Chaoui, F. Giri and M. M Saad
\textit{Adaptive Control in Presence of Input Saturation Constraint, an Input-Output approach}. 
1997 European Control Conference (ECC)

\bibitem{Valluri} 
Sairam Valluri and Vikram Kapila
\textit{Geometric Control of Input Saturated Systems with Guaranteed Closed-Loop Performance and Stability}. 
Proceedings of the American Control Conference

\bibitem{GENESIO} 
Min Cao and Christoforos Hadjicostis
\textit{Distributed Algorithms for Voronoi Diagrams and Applications in Ad-hoc Networks}. 

\bibitem{Sachan} 
Kapil Sachan and Radhakant Padhi
\textit{Barrier Lyapunov Function Based Output-constrained Control of Nonlinear Euler-Lagrange Systems}. 
2018 15th International Conference on Control, Automation, Robotics and Vision (ICARCV)

\bibitem{GENESIO} 
Roberto Genesio, Michele Tartaglia, Member IEEE and Antonio Vicino
\textit{On the Estimation of Asymptotic Stability Regions: State of the Art and New Proposals}. 
IEEE TRANSACTIONS ON AUTOMATIC CONTROL, VOL. AC-30. NO. 8, AUGUST 1985











\end{thebibliography}
 
%	\\ - [2] Cheng Song, Lu Liu, and Gang Feng. Coverage control for mobile sensor networks with input saturation. Unmanned Systems, 4(01):15{21, 2016.
